---
title: "Blockchain, marketing and the metaverse"
format: html
editor: visual
execute:
  echo: false
---


```{r settings}
options(stringsAsFactors = FALSE)
invisible(Sys.setlocale(category = "LC_ALL", locale = "C"))
set.seed(42)
```

```{r packages}

# install.packages("pacman")
pacman::p_load(magrittr, data.table, stringr, lubridate, # overviewR,
               ggplot2, MetBrewer, knitr,
               qdapRegex, tm, sentimentr, lexicon, radarchart, tidytext, #qdap
               pbapply, lda, LDAvis)
```

```{r design}
# ggplot layout
layout <- theme(panel.background = element_rect(fill = "transparent", color = NA),
                plot.background = element_rect(fill = "transparent", color = NA),
                panel.grid = element_blank(),
                panel.grid.major.y = element_blank(),
                legend.key = element_rect(fill = "transparent"),
                axis.line = element_line(size = 0.25),
                axis.ticks = element_line(size = 0.25),
                plot.caption = element_text(colour = "#555555"),
                legend.title = element_blank()
)

# color
# colors <- met.brewer(name="Tam",n=7,type="discrete")
cPrimary = "#00802F"
cSecondary = "#EB6969"
cInfo = "#FFF04B"
cDanger <- "#EB6969"
```

```{r helpers}
# error handling wrapper function for tolower()
tryTolower <- function(x){
  y = NA
  try_error = tryCatch(tolower(x), error = function(e) e)
  if (!inherits(try_error, 'error'))
    y = tolower(x)
  return(y)
}

# remove blanks
blankRemoval<-function(x){
  x <- unlist(strsplit(x,' '))
  x <- subset(x,nchar(x)>0)
  x <- paste(x,collapse=' ')
}

# always use the singular of nft
singularNFT <- function(x){
  str_replace_all(string = x,
                  pattern = "nfts",
                  replacement = "nft")
}

# wrapper 
cleancorpus <- function(corpus, stopwords = customStopwords){
  corpus <- tm_map(corpus, content_transformer(tryTolower))
  corpus <- tm_map(corpus, removeWords, stopwords)
  corpus <- tm_map(corpus, removePunctuation) # also removes "#" and "@"
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, content_transformer(singularNFT))
  # corpus <- tm_map(corpus, stemDocument) # debatable step
  return(corpus)
}
```

```{r periods}
startDate <- as.Date("2022-03-23")
endDate   <- as.Date("2022-03-27")
```

# Background

Following the Milan Fashion Week, the first ever Metaverse Fashion Week (MVFW) was hosted on [Decentraland](https://decentraland.org/blog/announcements/metaverse-fashion-week-is-here/) between `r startDate` and `r endDate`. It offered classic runways and panel discussion as well as flagship stores of well known brands (such as _Estée Lauder_, _Philipp Plein_ or _Forever 21_), pop-up stores and after show parties. 

Importantly, visitors were able to buy NFTs that match physical products. Some NFTs were even shipped with vouchers that could be redeemed for the respective physical twin.

# Data

::: {.callout-tip icon="false"}
## TWINT Querry

The data described below may stem from the following query using [TWINT.](https://github.com/twintproject/twint) 
:::


```{python queryData}
#| eval: false
#| echo: true

import twint

# Configure
config = twint.Config()
config.Search = "mvfw"
config.Lang = "en"
config.Since = "2021-11-27 00:00:00"
config.Until = "2022-04-26 00:00:00"
# config.Limit = 100
Store_csv = True
config.Output = "tweetMetaverseFashionWeek.csv"

# Run
twint.run.Search(config)
```

```{r readData}
tmp <- read.csv("../studentProject/tweetMetaverseFashionWeek.csv") %>% 
  data.table()
```

## Refactor

```{r transformData}
# String clean up 
tmp[, tweet := iconv(tweet, "latin1", "ASCII", sub = "")]
tmp[, tweet := rm_url(tweet,                    # remove URLs
                      pattern = pastex("@rm_twitter_url", "@rm_url"))]
# requires qdap
# tmp[, tweet := bracketX(tweet , bracket="all")] # rm strings in between parentheses, and other brackets
# tmp[, tweet := replace_abbreviation(tweet)]     # replaces a.m. to AM etc

# subset english sample of unique tweets
en <- tmp[language == "en"] %>% unique(by = "tweet")

# create distinc ID
en[, doc_id := .I]

# change date & time format
en[, created_at := str_sub(string = created_at,
                           start  = 1,
                           end    = 19) %>% ymd_hms()]
en[, date := dmy(date)]

# store mentions (@....)
en[, customMentions := str_extract_all(string = tweet,
                                       pattern = "@\\S+")]
en[customMentions == "character(0)", 
   customMentions := NA]

# define time frames
en[, timing := "before"]
en[date > startDate, timing := "during"]
en[date > endDate, timing := "after"]

en[, timing := factor(timing,
                      ordered = TRUE,
                      levels  = c("before", "during", "after"))]

# re-arrange data for corpus
data <- en[,
           .(doc_id,
             text = tweet,
             hashtags,
             cashtags,
             username,
             mentions,
             name,
             place,
             urls,
             photos,
             video,
             geo,
             created_at,
             timing,
             timezone,
             mentions,
             replies_count,
             retweets_count,
             likes_count,
             language,
             id,
             conversation_id,
             retweet_id)]

```

The data contains `r format(tmp[, .N], big.mark = ".", decimal.mark = ",")` rows, each representing a tweet.  Its columns represent some IDs, meta information about URLs, retweets, etc. as well as the tweets itself (from which I removed URLs using `qdapRegex::rm_url()`). The data was scraped for a period ranging from `r en[, min(date)]` to `r en[, max(date)]`.

I subset the data to focus on english tweets. In addition, I prune duplicated tweets. This leaves us with a [data.table](https://cran.r-project.org/web/packages/data.table/vignettes/datatable-intro.html) that has `r format(en[, .N], big.mark = ".", decimal.mark = ",")` rows that correspond to unique English tweets.

The metaverse fashionweek (MVFW) took place from March 24^th^ until March 27^th^. The following graph inspects the number of tweets posted in and around that time.

```{r overview}
tmp <- en[, .N, by = date]
tmp[, mvfw := FALSE]
tmp[date >= as.Date("2022-03-24") & date <= as.Date("2022-03-27"), mvfw := TRUE]

n <- tmp[mvfw == TRUE, sum(N)]

ggplot(data = tmp[date >= as.Date("2022-02-24") & date <= as.Date("2022-04-27")],
       mapping = aes(x = date, y = N)) +
  geom_line(color = "#00802F") +
  geom_area(fill = "#00802F", alpha = 0.66) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA)) +
  geom_vline(xintercept = startDate, col = "#FFFFFF") +
  geom_vline(xintercept = endDate, col = "#FFFFFF") +
  layout +
  theme(legend.position = "none") +
  labs(title = "Absolute number of unique english tweets per day",
       x = "Date",
       y = "",
       caption = paste0("The green shaded area represents MVFW period with a total of " ,n, " unique english tweets.",
                        "White lines mark start- and end date of the MVFW."))
```

As the following table shows, there are few usernames who are associated to quite a lot of posts. Simultaneously, there are many usernames, who have only posted one tweet (that ended up being in our data).

```{r numberOfTweets}
tmp <- data[, .N, by = username]
tmp %>% setorder(-N) %>% head(5) %>% kable(col.names = c("username", "number of tweets"))
singleTweetUsers <- tmp[N == 1, .N]
```

More precisely, there are `r tmp[N == 1, .N]` (or `r format(tmp[N == 1, .N] / tmp[, .N] * 100, digits = 2)`%) users with only one tweet in our data.

```{r withinSubjectsDesign}

A <- data[timing == "before", .(username, text, created_at)]
B <- data[timing == "after", .(username, text, created_at)]

# set the ON clause as keys of the tables:
setkey(A,username)
setkey(B,username)

# perform the inner join
C <- A[B, nomatch=0]

# get users who posted before and after
withinUsers <- C[, unique(username)]

within <- data[username %in% withinUsers]

setorder(within, username, created_at)

rm(list = c("A", "B", "C"))

# within[, .N, by = username]$N %>% min() # check the min number of rows per username
```

Moreover, we count `r within[, unique(username)] %>% NROW()` users with qualified tweets before _and_ after the MVFW. We can exploit the corresponding tweets for a within-subject-design, to display how the sentiment of tweeters changed over time (pre- and post-MVFW).

# Polarity Analyses

Given the available data and according to [this analysis plan](https://universitaetstgallen-my.sharepoint.com/personal/hauke_roggenkamp_unisg_ch/_layouts/15/doc.aspx?sourcedoc=%7Bf4cddff1-b1e0-4d63-987f-abc35284a2fa%7D&action=edit), I'll analyze tweets over time in what follows.

## Within-Subjects

We want to analyze tweets of people who posted before and after the MVFW and see whether their polarity or sentiment changed during the event. To get the corresponding data, I create two subsets of data: one with tweets from before (`A`) and one with tweets from after (`B`) the MVFS.
I then perform an inner join with these two tables which yields data (`C`) that only contains tweets of users who tweeted in both periods. I can then use these `withinUsers`s to create a `within` data.table by selecting only the `data` of these `username`s.

```{r within1to1}
# create da data.table that concatenates all pre-event tweets as well as post-event tweets by user. 
# withinCondensed <- within[, 
#                           .(text = toString(text)), 
#                           by = c("username", "timing")][timing != "during"]

pre <- within[timing == "before", 
              .(polarity = sentiment_by(text.var = text,
                                        by = username,
                                        polarity_dt = lexicon::hash_sentiment_jockers_rinker,
                                        valence_shifters_dt = lexicon::hash_valence_shifters,
                                        amplifier.weight = 0.8,
                                        n.before = 5,
                                        n.after = 2))]

post <- within[timing == "after", 
               .(polarity = sentiment_by(text.var = text,
                                         by = username,
                                         polarity_dt = lexicon::hash_sentiment_jockers_rinker,
                                         valence_shifters_dt = lexicon::hash_valence_shifters,
                                         amplifier.weight = 0.8,
                                         n.before = 5,
                                         n.after = 2))]

tmp1 <- pre[, .(username = polarity.username,
                preSent  = polarity.ave_sentiment,
                preCount = polarity.word_count)]

tmp2 <- post[, .(username = polarity.username,
                 postSent  = polarity.ave_sentiment,
                 postCount = polarity.word_count)]

withinPolarity <- tmp1[tmp2, on = .(username = username)]

withinPolarity[, diff := postSent - preSent]
```

```{r}

preavg  <- withinPolarity[, mean(preSent)]
postavg <- withinPolarity[, mean(postSent)]

tmp <- melt(withinPolarity, 
            id.vars = c("username"),
            measure.vars = c("preSent", "postSent"),
            variable.name = "timing",
            value.name = "sentiment")

ggplot(data = tmp,
       mapping = aes(x = sentiment, fill = timing)) +
  geom_density(alpha = 0.4, col = NA) +
  scale_y_continuous(expand = c(0, NA)) +
  scale_x_continuous(limits = c(-1, 1)) +
  geom_vline(xintercept = 0, size = 0.5) +
  geom_vline(xintercept = preavg, lty = 2, alpha = 0.5) +
  geom_vline(xintercept = postavg, lty = 2, alpha = 0.5) +
  layout +
  scale_fill_discrete(labels=c("pre MVFW", "post MVFW")) +
  theme(axis.line.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = "bottom") +
  labs(title = "Distribution of Polarity (Sentiment)",
       y = "Density", x = "Sentiment",
       caption = "Dashed lines mark the respective means.")
```

```{r}
sample.mean <- withinPolarity[, mean(diff)]

sample.n <- withinPolarity[, .N]
sample.sd <- withinPolarity[, sd(diff)]
sample.se <- sample.sd/sqrt(sample.n)

alpha = 0.05
degrees.freedom = sample.n - 1
t.score = qt(p=alpha/2, df=degrees.freedom,lower.tail=F)

margin.error <- t.score * sample.se
lower.bound <- sample.mean - margin.error
upper.bound <- sample.mean + margin.error
```


```{r}
# Calculate the mean and standard error
l.model <- lm(formula = diff ~ 1, 
              data = withinPolarity)

# Calculate the confidence interval
lb <- confint(l.model, level = 0.95)[1] %>% round(digits = 3)
ub <- confint(l.model, level = 0.95)[2] %>% round(digits = 3)

ggplot(data = withinPolarity,
       mapping = aes(x = diff)) +
  geom_density(alpha = 0.4, col = NA, fill = cPrimary) +
  scale_y_continuous(expand = c(0, NA)) +
  scale_x_continuous(limits = c(-1, 1)) +
  geom_vline(xintercept = 0, size = 0.5) +
  geom_vline(xintercept = lb, lty = 2, alpha = 0.5, col = "#FFFFFF") +
  geom_vline(xintercept = ub, lty = 2, alpha = 0.5, col = "#FFFFFF") +
  layout +
  theme(axis.line.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = "bottom") +
  labs(title = "Within Subject Polarity Differences",
       y = "Density", x = "Post-Event minus Pre-Event Polarity.",
       caption = paste0("Dashed white lines indicate 95% confidence intervall ranging from ", lb, " to ", ub, "."))
```


## Between Subjects

If we limit ourselves to users who (as far as we know) tweeted before and after the MVFW, we have to prune a lot of data. More precisely, we ignore `r round((1-within[, .N] / en[, .N])*100, digits = 1)`% of the available tweets.^[Because we focus on `r tmp[, .N]` users that have tweeted at least before and after the event.]

For this reason, it is worthwhile to also look into aggregate effects. As before, `sentiment_by` yields average polarities (`ave_sentiment`) across time periods.

```{r polarityByGroupTable}
sentiment_by(text.var = data[, get_sentences(text)],  # from sentimentr
             by = data[, timing],
             polarity_dt = lexicon::hash_sentiment_jockers_rinker,
             valence_shifters_dt = lexicon::hash_valence_shifters,
             amplifier.weight = 0.8,
             n.before = 5,
             n.after = 2) %>% 
  kable()
```

Using the same function, one can plot distributions, simply by calculating the polarity for each tweet.

```{r polarityByGroupViz}
temp <- sentiment_by(text.var = data[, get_sentences(text)],
                     by = data[, doc_id],
                     polarity_dt = lexicon::hash_sentiment_jockers_rinker,
                     valence_shifters_dt = lexicon::hash_valence_shifters,
                     amplifier.weight = 0.8,
                     n.before = 5,
                     n.after = 2) 

merge <- temp[data, on = .(doc_id=doc_id)]

ggplot(data = merge,
       mapping = aes(x = ave_sentiment,
                     fill = timing)) +
  geom_density(alpha = 0.4, col = NA) +
  scale_y_continuous(expand = c(0, NA)) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(title = "Polarity distribution by time frame",
       caption = "Using lexicon::hash_sentiment_jockers_rinker.",
       x = "Polarity", y = "Density") +
  layout +
  theme(axis.line.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = "bottom")
```

Both, the table as well as the figure show considerable differences.  The distributions illustrate, however, that there are many tweets (across all time periods) with a neutral polarity. In addition, relatively few have a negative sentiment.


# Sentiment Analysis: Emotional States

In addition, we can run another sentiment analysis using [Plutchik Wheel](https://www.jstor.org/stable/27857503).

## Between Subjects

Luckily, the `lexicon` package contains a `nrc` lexicon that is tidy (which saves me some lines of code). I'll eventually merge it with a tidy document term matrix (DTM), that I'll create next.

```{r lexicon}
nrc_emotions <- lexicon::hash_nrc_emotions
# lexicon::hash_internet_slang
# nrc_emotions %>% head() %>% kable()
```

```{r stopwords}
customStopwords <- c(stopwords("english"), "amp",
                     "mvfw", "fashion", "week", "fashionweek",
                     "metaverse", "decentraland")
```

The DTM is created using a loop that combines a long character for all of a news outlet's articles. The combined vector is then being turned into a corpus, cleaned and transferred into a matrix. After renaming the rows (using the outlet's names), the matrix is turned into a DTM again and then tidy-ed.

```{r tidyDTM}
corpus <- DataframeSource(data) %>% VCorpus() %>% cleancorpus()

timeFrames <- unique(data$timing)
container <- c()
for(time in timeFrames){
  temp <- subset(corpus, meta(corpus)$timing == time)
  texts <- sapply(temp, content) %>% 
    paste(collapse = " ")
  container <- c(container, texts)
}

corpusByTimeFrame <- VectorSource(container) %>% VCorpus() %>% cleancorpus()

matDTM <- DocumentTermMatrix(corpusByTimeFrame) %>% as.matrix()
rownames(matDTM) <- timeFrames

DTM <- as.DocumentTermMatrix(matDTM, weighting = weightTf)
tidyCorp <- tidy(DTM) %>% data.table()
```

The resulting `tidyCorp` can now be merged with the `nrc_emotions` lexicon. Because `data.table` processes a full join, I'll remove all the rows that do not contain any `count` information.

```{r mergeLexiconDTM}
sent <- tidyCorp[nrc_emotions, on = .(term = token)][!is.na(count)]
```

We can then use the data and create a radar chart. The process is a little ugly, because `chartJSRadar()` requires a list and I have not found an elegant way to create one. 


```{r vizRadar}
labs <- sent[order(emotion), unique(emotion)]
scores <- list(
  "before" = sent[document == "before", 
                  .N, 
                  by = emotion][order(emotion), N]/sent[document == "before", .N],
  "during" = sent[document == "during",
                  .N,
                  by = emotion][order(emotion), N]/sent[document == "during", .N],
  "after" = sent[document == "after", 
                 .N, 
                 by = emotion][order(emotion), N]/sent[document == "after", .N]
)

chartJSRadar(scores = scores, labs = labs) #, maxScale = 0.25)

```

```{r vizLollipop}
A <- sent[,
     .(N_emotions = .N),
     by = c("emotion", "document")]
B <- sent[,
     .(N_documents = .N),
     by = c("document")]

C <- B[A, on = .(document = document)]

C[, share := N_emotions / N_documents]

ggplot(data = C,
       mapping = aes(x = emotion, y = share, col = document)) +
  geom_point() +
  layout
```
We can follow the same procedure using the bing lexicon.

```{r}
bing <- get_sentiments("bing") %>% data.table()
sent <- tidyCorp[bing, on = .(term = word)][!is.na(count)] %>% data.table()

sent[,
     N_documents := .N,
     by = c("document")]

sent[, freq := count/ N_documents]
setorder(sent, document, sentiment, -freq)

bingViz <- function(bSent = "positive",
                    timing = "before",
                    n = 10){
  
  color <- cPrimary
  if(bSent == "negative"){
    color <- cDanger
  }
  
  ggplot(data = sent[sentiment == bSent & document == timing] %>% head(n),
       mapping = aes(x = reorder(term, freq),
                     y = freq)) +
  geom_bar(stat = "identity", fill = color) +
  scale_y_continuous(expand = c(0, NA)) +
  labs(title = paste0(str_to_title(bSent), "ly loaded terms ", timing, " the event"),
       y = "Term", x = "Frequency",
       caption = "Using the bing lexicon.") +
  layout +
  coord_flip() +
  theme(axis.line.x = element_blank())
}

bingViz("positive", "before")
bingViz("positive", "during")
bingViz("positive", "after")

bingViz("negative", "before")
bingViz("negative", "during")
bingViz("negative", "after")

```

# Topics

```{r}
# Extract the clean text
txt <- unlist(pblapply(corpus, content))

# Remove any blanks
txt <- pblapply(txt, blankRemoval)

# Lexicalize
txtLex <- lexicalize(txt)

# Examine the vocab or key and value pairing between key ()
head(txtLex$vocab, 15) 
length(txtLex$vocab)  
head(txtLex$documents[[1]][,1:12])
head(txtLex$documents[[20]])

# Corpus stats
txtWordCount  <- word.counts(txtLex$documents, txtLex$vocab)
txtDocLength  <- document.lengths(txtLex$documents)
```

```{r}
# Cluster
k       <- 3 
numIter <- 25 
alpha   <- 0.02 
eta     <- 0.02 
fit <- lda.collapsed.gibbs.sampler(documents      = txtLex$documents, 
                                   K              = k, 
                                   vocab          = txtLex$vocab, 
                                   num.iterations = numIter, 
                                   alpha          = alpha, 
                                   eta            = eta, 
                                   initial        = NULL, 
                                   burnin         = 0,
                                   compute.log.likelihood = TRUE)

# Prototypical Document
proto <- top.topic.documents(fit$document_sums, 1) # top 3 docs (rows) within topics (cols)
for(i in proto){
  print(txt[[i]])
}
```

```{r}
# LDAvis params
# normalize the article probabilities to each topic
theta <- t(pbapply(fit$document_sums + alpha, 2, function(x) x/sum(x))) # topic probabilities within a doc will sum to 1

# normalize each topic word's impact to the topic
phi  <- t(pbapply(fit$topics + eta, 1, function(x) x/sum(x)))

ldaJSON <- createJSON(phi = phi,
                      theta = theta, 
                      doc.length = txtDocLength, 
                      vocab = txtLex$vocab, 
                      term.frequency = as.vector(txtWordCount))

serVis(ldaJSON)
```


```{r}
#| eval: false

# Topic Extraction
top.topic.words(fit$topics, 5, by.score=TRUE)

# Name Topics
topFive <- top.topic.words(fit$topics, 5, by.score=TRUE)
topFive <- apply(topFive,2,paste, collapse='_') #collapse each of the single topics word into a single "name"

# Topic fit for first 10 words of 2nd doc
fit$assignments[[2]][1:10]

# Tally the topic assignment for the second doc, which topic should we assign it to?
table(fit$assignments[[2]])

# What topic is article 2 assigned to?
singleArticle <- docAssignment(fit$assignments[[2]])

# Get numeric assignments for all docs
topicAssignments <- unlist(pblapply(fit$assignments,
                                    docAssignment))
topicAssignments

# Recode to the top words for the topics; instead of topic "1", "2" use the top words identified earlier
length(topicAssignments)
assignments <- recode(topicAssignments,
                      `0` = topFive[1],
                      `1` = topFive[2],
                      `2` = topFive[3],
                      `3` = topFive[4],
                      `4` = topFive[5])

```


# Frequent Terms and Associations

```{r}
freqs <- list()
for(t in data[, unique(timing)]){
  corpus <- DataframeSource(data[timing == t]) %>% VCorpus() %>% cleancorpus() # stopwords = stopwords("english")
  TDM <- TermDocumentMatrix(corpus, control = list(weighting = weightTf))
  tdm <- TDM %>% as.matrix()
  termFreq <- data.table(word = names(rowSums(tdm)),
                         frequency = rowSums(tdm))
  setorder(termFreq, -frequency)
  freqs[[t]] <- termFreq
}

freqs[["before"]] %>% head(10) %>% kable()
freqs[["during"]] %>% head(10) %>% kable()
freqs[["after"]] %>% head(10) %>% kable()
```

```{r}

wrapAssocs <- function(time = "before", term = "nft", cor = 0.2){
  corpus <- DataframeSource(data[timing == time]) %>% VCorpus() %>% cleancorpus(stopwords = stopwords("english"))
  TDM <- TermDocumentMatrix(corpus, control = list(weighting = weightTf))
  associations <- findAssocs(TDM, term, corlimit = cor)
  associations <- as.data.frame(associations)
  associations$terms <- row.names(associations)
  associations$terms <- factor(associations$terms, levels = associations$terms)
  associations %<>% data.table()
  associations
}

wrapAssocs(time = "before", term = "nft") %>% kable()
wrapAssocs(time = "during", term = "nft") %>% kable()
wrapAssocs(time = "after", term = "nft") %>% kable()
```

```{r}
```


# Preparation


```{r createCorpus}
corpus <- DataframeSource(data) %>% VCorpus() %>% cleancorpus()
```

```{r tdm}
tdm <- TermDocumentMatrix(corpus, control = list(weighting = weightTf)) %>% 
  as.matrix()

tmp <- rowSums(tdm)
frequencies <- data.table(terms = names(tmp),
                          frequency = tmp)
setorder(frequencies, -frequency)

head(frequencies, 10)
```
